Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-04 paper/ms.tex
Add caption to the range-deltaphi plot

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{Caption.}
\label{fig:range_deltaphi}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{The range of midplane heights encountered as a function of angular
width. At each angle $\phi$ from Figure~\ref{fig:midplane} we consider an
angular width of $\Delta \phi$ centered on $\phi$ and report the range of
midplane heights within that width. We repeat the procedure for each $\phi$
and plot the result as translucent gray lines. We also plot the mean range as
a solid blue line and the $\pm1\sigma$ lines as dashed blue lines. The upper
$x$-axis shows the chord length from the position $\phi$ to
$\pm\Delta\phi/2$.}
\label{fig:range_deltaphi}
\end{figure*}
